Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-03 alloscore_manuscript/supplement.rnw

In the case ($\bullet$), we can immediately take 
$\tau^{\star}=\tau_U$ as the probability level defining the allocation Bayes act.
In the cases
($\bullet\!-$), and ($-\!\bullet$), which imply the presence of a point mass in one or more of the 
component forecasts adjacent to a region of zero density in all components, we can take $\tau^{\star}=\tau_U$ or $\tau_L$, 
respectively, as the representing probability level and find Bayes acts within the set 
$\undertilde{\bm{F}}^{-1}(\tau^{\star})$ (by solving the linear equation 
$\sum_{x \in \undertilde{\bm{F}}^{-1}(\tau^{\star})}x_i = K$).

Otherwise, by evaluating $TQ_F$ at $\tau_M = \frac{1}{2}\left(\tau_L + \tau_U\right)$ we can replace $I_1$ with the interval
\begin{align}
I_2 = 
\begin{cases}
[\tau_L, \tau_M] & \text{ if } K \leq q^{+}_{F_T,\tau_M} \\
[\tau_M, \tau_U] & \text{ if } K > q^{-}_{F_T,\tau_M}.
\end{cases}
\end{align}

>>>>

In the case ($\bullet$), we can immediately take 
$\tau^{\star}=\tau_U$ as the probability level defining the allocation Bayes act.
In the cases
($\bullet\!-$), and ($-\!\bullet$), which imply the presence of a point mass in one or more of the 
component forecasts adjacent to a region of zero density in all components, we can take $\tau^{\star}=\tau_U$ or $\tau_L$, 
respectively, as the representing probability level and find Bayes acts within the set 
$\undertilde{\bm{F}}^{-1}(\tau^{\star})$ (by solving the linear program 
$\sum_{x \in \undertilde{\bm{F}}^{-1}(\tau^{\star})}x_i = K$).

Otherwise, by evaluating $TQ_F$ at $\tau_M = \frac{1}{2}\left(\tau_L + \tau_U\right)$ we can replace $I_1$ with the interval
\begin{align}
I_2 = 
\begin{cases}
[\tau_L, \tau_M] & \text{ if } K < q^{-}_{F_T,\tau_M} \\
[\tau_M, \tau_U] & \text{ if } K \geq q^{-}_{F_T,\tau_M}.
\end{cases}
\end{align}
